---
title: "Team"
---

# Leadership team 

**Directors:** the directors are in charge of overall leadership of
SEEC; i.e. to give the group strategic direction. The directors will
make sure that the leadership team works together effectively to further
SEEC’s interest. The directors represent SEEC in dealings with the
university, outside partners and in research collaborations (even though
the latter can be delegated in cases, e.g. if a specific collaboration
is led by a different SEEC member). The directors also look after any
leadership matter that may come up and that is not specifically part of
any of the other portfolios.

**Research and students (Head of Research):** this portfolio assumes
responsibility for SEEC’s support structures for research and
postgraduate students. The person heading up this portfolio will give it
strategic direction by keeping an eye on whether the structures are
still fulfilling their purpose and revise or add new structures that
help SEEC carry out research and train students successfully. At the
moment, these structures include research meetings, writing retreats,
and the annual SEEC symposium. The person heading up this portfolio also
ensures that the student list is up-to-date. A need at the moment is to
develop guidelines that help students complete on time and to minimize
the time they (and their supervisors) spend on admin, e.g. develop a
template for the annual MOU/PPA process, a pack with detailed info on
how to navigate registration, funding, hand-in, animal ethics, research
ethics, data management plans, effective literature search, etc.

**Outreach (Head of Outreach):** the Outreach portfolio is responsible
for growing SEEC’s visibility and profile. The person heading up this
portfolio will give it strategic direction by keeping an eye on whether
the structures are still fulfilling their purpose and revise or add new
structures that help growing SEEC’s visibility and profile. At the
moment, these structures include the stats course, the web site / social
media accounts, the toolbox seminars, the noticeboard and corridor
around the SEEC offices and other marketing initiatives (e.g. pamphlet,
banner, etc.). A need at the moment is to refresh the publications on
the notice board and to think about how we could better use the walls of
our corridors to mark SEEC’s presence there (posters, SEEC logo on wall,
etc.).

**Fundraising / grants (Head of Fundraising):** there is a need for more
strategic thinking about funding for SEEC’s core functions. In addition,
this portfolio puts in place and maintains structures that help SEEC
members find funding opportunities and submit successful grant
applications for projects.

**Operations (Head of Operations):** this portfolio could be split
between an academic and a part-time (say 20%) administrator, or – if we
can raise the necessary funding and find the right person – be covered
by a part-time (50% or even more) administrator. Tasks include: organise
meetings and take minutes, practical side of reporting (including
setting up reporting templates for annual reports), look after SEEC
offices (6.74 and 6.75), HR admin, organise stats course, admin support
to students, organise SEEC symposium, organise social events, finance
admin, practical support for proposal writing.

# Affiliations

The SEEC leadership team decided to present our members in three groups: leadership team, rest of the core team and affiliates. We used the below guidelines on what is expected of the different categories of affiliation to decide who should be a core member vs affiliate. This was circulated to the all SEEC members for feedback and adjusted on the website accordingly. The curren team and affiliations can be seen in Table @tab:affaca.

**SEEC Academics and Postdoctoral Fellows (Core Team)**

-   These are people who view the success of SEEC and their own academic
    success as being connected to some degree.
-   They attend the monthly SEEC staff meetings as this is where the
    direction of SEEC is developed.
-   Take a leadership role or assist with the organising of the various
    facets of SEEC e.g. Stats Toolbox, research seminars.
-   Make an effort to contribute to raising funds to support SEEC core
    activities and shared resources.
-   Benefit from shared SEEC resources (admin support, computers, office
    space).
-   Contribute ideas when called upon to do so.
-   Attend the annual SEEC Student symposium if at all possible.
-   Make every reasonable effort to attend research meetings.
-   List SEEC as an affiliation on any papers written or presentations
    given.
-   Contribute to the SEEC annual report.
-   Actively collaborate with other SEEC members.
-   If not based at a South African University, SEEC core members need
    to be Honorary Research Associates.
-   Are on the seec-staff-l mailing list.

\newpage 

**SEEC Postgraduates**

-   These are students whose research project and interests fall within
    the parameters of Statistics in Ecology, Environment and
    Conservation and whose supervisor is supportive of the connection to
    the group. They have a (co)supervisor who is part of the core group
    or an Affiliated Academic.
-   Present at least two talks each year. One will be at the annual SEEC
    symposium and the other will be at the research meetings held at
    three-weekly intervals.
-   Attend the annual SEEC Student symposium.
-   Attend all research meetings (arrangements can be made for SEEC
    students who are not based in Cape Town).
-   List SEEC as an affiliation on any papers written or presentations
    given.
-   Are on the seec-all-l mailing list.

**SEEC Affiliated Academic**

-   These academics are SEEC members but not willing or able to
    contribute to the same degree as a core team member, either because
    of commitments with other research groups or because their area of
    interest only overlaps partly with SEEC’s vision.
-   Add their SEEC affiliation to their publications where appropriate.
-   Willing to work with the group, contribute to meetings and joint
    projects, bring opportunities to the attention of the group and
    promote the group in conversations if the opportunity arises.
-   Can benefit from shared SEEC resources if they contribute funding.
-   Postgraduate students of affiliated academics can be SEEC
    postgraduate students.
-   Can be SEEC Honorary Research Associates if not based at a South
    African university.
-   Attend the SEEC student symposium and research meetings if possible.
-   Are on the seec-staff-l mailing list.

**SEEC Undergraduates**

-   Undergraduate students who are interested in the work we do at SEEC.
-   They can be involved in research projects.
-   They are encouraged to participate in the Research Meetings and to
    attend the student symposium.
-   They can be mentored by SEEC Postgraduates or academics.
-   Are on the seec-all-l mailing list.

**SEEC Advisory Board**

-   Attend and give inputs at board meetings.
-   Give inputs and advice when called upon.
-   Are being updated about SEEC activities through the annual report
    and at meetings.

**SEEC Partners**

-   Academics or scientists working at a university or research
    organisation who collaborate with the SEEC core team, be it as
    co-supervisors, or collaborators on projects and funding
    applications.
-   These academics are not formally part of the SEEC team and are not
    expected to list SEEC as an affiliation on papers and presentations.
-   Can be consulted for inputs on SEEC strategy or projects.
-   Can be on the the seec-friends-l mailing list.

**SEEC Friends**

-   Anyone who is interested in what we do and would like to be informed
    of seminars (Stats Toolbox) and courses.
-   There is no obligation or commitment either on part of SEEC or the
    Friends.
-   Are on the seec-friends-l mailing list or keep themselves in the
    loop through the SEEC facebook page, twitter or web site.


```{r}
library(lubridate)
library(DT)
library(dplyr)
library(googlesheets4)

source("R/data.R")
d <- seec_read_data()

updated <- with_tz(Sys.time(), "Africa/Johannesburg")
```

**Last updated:** `r format(updated, "%Y-%m-%d %H:%M %Z")`

```{r}
DT::datatable(
  d$coreteam,
  rownames = FALSE,
  filter = "top",
  extensions = "Buttons",
  options = list(
    dom = "Bfrtip",
    buttons = c("copy", "csv", "excel"),
    pageLength = 25,
    scrollX = TRUE
  )
)
```
